\begin{thebibliography}{99}
	\bibitem{cpp}	
	Bjarne Stroustrup:
	\emph{A C++ programozási nyelv}, 
	Kiskapu, 2001, [1305], 
	ISBN 963 9301 17 5 ö

	\bibitem{gsdgtl} 
	Zoltán Porkoláb, Róbert Kisteleki: 
	\emph{Alternative Generic Libraries}, 
	ICAI'99 4th International Conference on Applied Informatics, 
	Ed: Emõd Kovács et al., Eger-Noszvaj, 
	1999, 
	[79-86]
		
	\bibitem{tmpboost} 
	David Abrahams, Aleksey Gurtovoy: 
	\emph{C++ Template Metaprogramming - 
	Consepts, Tools, and Techniques from Boost and Beyond}, 
	Addison Wesley Professional, 
	2004, 
	ISBN 0-321-22725-5
	
	\bibitem{tij} 
	Bruce Eckel, 
	\emph{Thinking in Java (3rd Edition) }, 
	Prentice Hall PTR, 
	2002, [1119], ISBN-10: 0131002872
	
	\bibitem{boost}
	\emph{Boost C++ Libraries}\\
	\verb"http://www.boost.org/libs/libraries.htm"\\
	2007. május 30.
	
	\bibitem{boost_mpl}
	\emph{The Boost MPL Library}\\
	\verb"http://www.boost.org/libs/mpl/doc/index.html"\\
	2007. május 30.
	
	\bibitem{boost_typetraits}
	\emph{Boost.TypeTraits}\\
	\verb"http://www.boost.org/doc/html/boost_typetraits.html"\\
	2007. május 30.
	
	\bibitem{boost_staticassert}
	\emph{Boost.StaticAssert}\\
	\verb"http://www.boost.org/doc/html/boost_staticassert.html"\\
	2007. május 30.
		
	\bibitem{haladocpp}
	Dr. Zoltán Porkoláb: \emph{Advanced C++ Lessons}\\
	\verb"http://aszt.inf.elte.hu/~gsd/halado_cpp/"\\
	2007. május 30.
	
	\bibitem{cgal}
	\emph{Computational Geometry Algorithm Library -- CGAL} \\
	\verb"http://www.cgal.org/"\\
	2007. május 30.
	
	\bibitem{vtl}
	\emph{View Template Library -- VTL} \\
	\verb"http://www.zib.de/weiser/vtl/"\\
	2007. május 30.
	
	\bibitem{gtldraw} 
	Vatai Emil:	\emph{GTL Draw rajzolóprogram}, \\
	\verb"http://gtldraw.googlecode.com/svn/trunk/"
	2007. május 30. 
	
\end{thebibliography}
